### 2014-04-24 msc-thesis/chapters/3/sec-apie.tex
MSC final version.

In this study, I examine the notions of software change trends, specifically those trends around major releases. Change trends are trends which indicate
a likelihood for a change type to occur around a certain event. Change trends have been used to detect
stability in core architecture~\cite{Wermelinger:2008:AEE} as well as evolving dependencies~\cite{Businge:2010:ESE}.
With the power of major release points in open source projects as a starting point for project stability and the understanding that change trends can
be leveraged to detect stability and the proneness of indirect conflicts, this study investigates the question:

>>>>

In this study, I examine the notions of software change trends, specifically those trends around major releases. Change trends are trends which indicate
a likelihood for a change type to occur around a certain event. Change trends have been used to detect
stability in core architecture~\cite{Wermelinger:2008:AEE} as well as evolving dependencies~\cite{Businge:2010:ESE}.
This study was conducted in order to address the results of Study 3 which identified that indirect conflicts are likely to occur more
before a major release (i.e. stable point in the code). I look to find the context in which trends occur in order to support
indirect conflict tools in their context for when indirect conflicts are more likely to occur.
With the power of major release points in open source projects as a starting point for project stability and the understanding that change trends can
be leveraged to detect stability and the proneness of indirect conflicts, this study investigates the question:

### 2014-04-24 msc-thesis/chapters/3/sec-iced.tex
MSC final version.

\subsection{Threats to Validity}
Because of the exploratory nature of this work, I chose Grounded Theory as my research method, which has some implications regarding the
limitations and threats to validity of this study. While I achieved high saturation regarding the topics focused on in this study, other
populations studied from outside of this studies participants may add new insights into the pool of findings. As a result of this, findings
from this study may only relate to developers or managers from the projects I studied.

>>>>

\subsection{Threats to Validity}
Because of the exploratory nature of this work, I chose Grounded Theory as my research method, which has some implications regarding the
limitations and threats to validity of this study. Inter rater reliability was not used due to a time constraint which means
that the code from open and axial coding have not been confirmed by a separate source.
While I achieved high saturation regarding the topics focused on in this study, other
populations studied from outside of this studies participants may add new insights into the pool of findings. As a result of this, findings
from this study may only relate to developers or managers from the projects I studied. The saturation indicated here regards the majority
results reached in this study. Since only 19 developers were interviewed, saturation was reached when majority agreed upon
trends emerged in the results, thus further interviews did not have to be conducted. This is different from saturation of edge or
unique cases often found in other qualitative research where the goal is to find all cases of a phenomenon where this study
was only looking for majority cases.
